---
title: "Database Round Up"
author: "Palmer Lab: Bonnie Lin"
output: pdf_document
date: "`r format(Sys.time(), '%d %B, %Y')`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)

# setwd("~/Dropbox (Palmer Lab)/Palmer Lab/Bonnie Lin/github/Mitchell_U01DA046077/QC")
# mitchell_genotyping <- flowcell_df %>% left_join(., WFU_Mitchell_test_df[, c("cohort", "rfid")], by = "rfid") %>% subset(!is.na(cohort)) ## add source, consider reorganization
# save(WFU_Mitchell_test_df, discounting_filenames, mitchell_shipments_spleen_df, mitchell_shipments_ceca_df, mitchell_genotyping, mitchell_macro_xl_df, file = "Mitchell_data.RData")
load(file = "Mitchell_data.RData")
```

## For Suzanne Mitchell


Below you will find the number of records that I have for your experiments, broken down by cohorts.


### \# of IDs from Wake Forest shipment sheets

```{r wfu-master, echo = F}
WFU_Mitchell_test_df %>% select(cohort) %>% table()
```

### \# of subjects in raw data

These were extracted from the text files in *Suzanne_Mitchell_U01/Data-discounting*

```{r raw-data, echo = F}
data.frame(filename = discounting_filenames) %>% 
  mutate(cohort = str_match(filename, "Ship\\d+")[,1],
         subject = str_match(filename, "Subject (.*?)\\.txt")[,2]) %>% # extract from filename 
  mutate(cohort = str_pad(parse_number(cohort), 2, "left", "0")) %>% # wrangle to uniform format 
  distinct(subject, cohort) %>% 
  select(cohort) %>% table()
```

### \# of subjects in excel data

These were extracted from the macro sheets in *Suzanne_Mitchell_U01/Protocol-materials/DD-programs/Data-Analysis-Information*

```{r xl-data, echo = F}
mitchell_macro_xl_df %>% mutate(subject = str_extract(filename, "Subject \\d+")) %>% distinct(cohort, subject) %>% select(cohort) %>% table()
```

### \# of IDs from tissue shipments

Spleens
```{r, echo = F}
mitchell_shipments_spleen_df %>% 
  mutate(cohort = str_match(sheet, "Shipment\\d+")[,1],
         cohort = str_pad(parse_number(cohort), 2, "left", "0")) %>% 
  distinct(rfid, cohort) %>% 
  select(cohort) %>% table()
```

Ceca
```{r, echo = F}
mitchell_shipments_ceca_df %>% 
  mutate(cohort = str_match(sheet, "Shipment\\d+")[,1],
         cohort = str_pad(parse_number(cohort), 2, "left", "0")) %>% 
  distinct(rfid, cohort) %>% 
  select(cohort) %>% table()
```


### \# of subjects in genotyping pipeline

This is the number of animals we are currently genotyping. 

```{r genotyped, echo = F}
mitchell_genotyping %>% distinct(rfid, cohort) %>% select(cohort) %>% table()
```
