---
title: "Database_RoundUp"
author: "Palmer Lab: Bonnie Lin"
output: pdf_document
date: "`r format(Sys.time(), '%d %B, %Y')`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)

# setwd("~/Dropbox (Palmer Lab)/Palmer Lab/Bonnie Lin/github/Mitchell_U01DA046077/QC")
# mitchell_genotyping <- flowcell_df %>% left_join(., WFU_Mitchell_test_df[, c("cohort", "rfid")], by = "rfid") %>% subset(!is.na(cohort)) ## add source, consider reorganization
# save(WFU_Mitchell_test_df, discounting_filenames, mitchell_shipments_spleen_df, mitchell_shipments_ceca_df, mitchell_genotyping, file = "Mitchell_data.RData")
load(file = "Mitchell_data.RData")
```

## R Markdown

Broken down by cohort

### \# of wake forest rfids 

Cohort breakdown 
```{r wfu-master, echo = F}
WFU_Mitchell_test_df %>% select(cohort) %>% table()
```

### \# of subjects in raw data

Cohort breakdown
```{r raw-data, echo = F}
data.frame(filename = discounting_filenames) %>% 
  mutate(cohort = str_match(filename, "Ship\\d+")[,1],
         subject = str_match(filename, "Subject (.*?)\\.txt")[,2]) %>% # extract from filename 
  mutate(cohort = str_pad(parse_number(cohort), 2, "left", "0")) %>% # wrangle to uniform format 
  distinct(subject, cohort) %>% 
  select(cohort) %>% table()
```

### \# of subjects in excel data

### \# of tissue shipments

Spleen cohort breakdown
```{r, echo = F}
mitchell_shipments_spleen_df %>% 
  mutate(cohort = str_match(sheet, "Shipment\\d+")[,1],
         cohort = str_pad(parse_number(cohort), 2, "left", "0")) %>% 
  distinct(rfid, cohort) %>% 
  select(cohort) %>% table()
```

Ceca cohort breakdown
```{r, echo = F}
mitchell_shipments_ceca_df %>% 
  mutate(cohort = str_match(sheet, "Shipment\\d+")[,1],
         cohort = str_pad(parse_number(cohort), 2, "left", "0")) %>% 
  distinct(rfid, cohort) %>% 
  select(cohort) %>% table()
```


### \# of animals in genotyping pipeline

Cohort breakdown
```{r genotyped, echo = F}
mitchell_genotyping %>% distinct(rfid, cohort) %>% select(cohort) %>% table()
```

## Experiments by Cohorts

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
